Scheeper's Meager-NWD Game and the Menger Game

### 2014-06-04 phd/dissertation/chapter3.tex
almost finished with chapter: need to finish game equivalency proof and complete sketch for the simpler game

We aim to show that $\pl F \codewin \pfgame\kappa$ for all
$\kappa$.

\begin{thm}
  Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
  Then $\pl F \codewin PF_{F,C}(\kappa)$.
\end{thm}

@@

\begin{thm}
  Let $\kappa$ be the limit of cardinals $\kappa_n$ such that
  $\cf{[\kappa_n]^{\leq\omega}}=\kappa_n$.
  Then $F \codewin \pfgame{\kappa}$.
\end{thm}

\begin{thm}
  $F\codewin\pfgame{\kappa}$ for all cardinals $\kappa$.
\end{thm}

>>>>

\begin{thm}
  Let $\cf{[\kappa]^{\leq\omega}}=\kappa$.
  Then $\pl F \codewin \pfgame\kappa$.
\end{thm}

@@

  (TODO: The above result is cute, but unnecessary due to the below.)

\begin{thm}
  $\pl F \codewin \pfgame{\kappa}$ for all cardinals $\kappa$.
\end{thm}

\begin{proof}
  TODO: Fill in sketch.

  SKETCH: For each cardinal
  $\kappa$, assume $F\codewin\pfgame\lambda$ for $\lambda<\kappa$. Always
  cover the upper bound of $\pl O$'s moves if possible, or use a trick
  assuming $\cf\kappa=\omega$.
\end{proof}
